---
title: KTRUTILS Package
author: Kendall Tauser
date: May 2nd, 2024
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{thing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# What is this?

What are KTRUTILS? This is a set of R utilities that I am originally creating for Applied Statistical Methods in Spring of 2024. But, hopefully this library can have a variety of useful statistical things that I can use in the future.

## Installation

You can install this package (although I am not sure why you would want to) via devtools directly, or pick your git install method of choice beyond this.

```{r}
# devtools::install_github("fire833/KTRUTILS")
```

# Examples of functions

```{r}
set.seed(30000)
library(ktrutils)

get_z(rnorm(50, 20, 5))

get_mss(rnorm(50, 20, 5), 20)

get_table_with_margins(c(3, 4, 5, 6), c(1, 2, 3, 4))

get_permutations(30, 5)
```

# View of loaded dataset

```{r}
data(fire)
head(fire)
```
